---
title: DANL Project
subtitle: "nflfastR"
author: 
  - Name Jessica Horst

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```

# Introduction

About this project :clap:

the purpose of this project is to show our understanding of the Rstudio and Quarto.


# Data

The data.frame `nflfastR` comes with a set of functions to access NFL play-by-play data and team rosters. nflfastR comes with a set of functions to access NFL play-by-play data and team rosters. 


## Summary Statistics

```{r}

```

```{r}
#| results: asis
#| echo: false

```


```{r}
skim(mpg) %>% 
  select(-n_missing)
```


## Expected Points calculator 

this is how we can find the Expected Points on a drive beginning following a touchback has changed over time. We could compare the most recent four years to the expectation for playing in a dome


