---
title: DANL Project
subtitle: "Global Shark Attack Incidents"
author: 
  - Name Jessica Horst

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```

# Introduction

About this project :clap:

the purpose of this project is to show our understanding of the Rstudio and Quarto.


# Data

The Global Shark Attack Data is a comprehensive dataset that provides daily updated records of shark attack incidents worldwide. It offers valuable information on various aspects of each incident, including the date and location of the attack, specific details about the activity the victim was engaged in at the time, and whether it resulted in a fatality or not. With additional columns such as age, injury description, and even the name of the victim involved, this dataset aims to inform people about the risks associated with coastal water
activities.
:shark:

## Summary Statistics

```{r}
sharks <- read.csv("C:\\Users\\Jhors\\OneDrive\\Documents\\Data Analytics\\GSAF5.xls.csv")
```

```{r}
#| results: asis
#| echo: false

```

## Q1a


```{r}

```




